The \Rpackage{eisa} and \Rpackage{biclust} packages

### 2014-03-26 eisa/inst/doc/EISA_biclust.Rnw
Fix EISA biclust vignette for new biclust
Because it creates different biclusters and we
ended up with an empty set.

The \Rfunction{gograph} and \Rfunction{gographPlot} functions 
create a plot of the part of the Gene Ontology tree that contains 
the enriched categories. See Fig.~\ref{fig:gotree}.
<<psoptions,results=hide,echo=FALSE>>=
ps.options(fonts=c("serif", "mono"))
@
<<GOtreeplot,eval=FALSE>>=
library(GO.db)
GO <- ISAGO(modules)
gog <- gograph(summary(GO$CC)[[2]])
summary(gog)
gographPlot(gog)
@ 
\begin{figure}
\centering
<<GOtreeplot-real,fig=TRUE,width=10,height=4,echo=FALSE>>=
<<GOtreeplot>>
@
\caption{Part of the Gene Ontology tree, Cellular Components ontology.
  The plot includes all terms with significant enrichment for the
  second module, and their parent terms, up to the most general term.
}
\label{fig:gotree}
\end{figure}

>>>>

The \Rfunction{gograph} and \Rfunction{gographPlot} functions 
create a plot of the part of the Gene Ontology tree that contains 
the enriched categories. See Fig.~\ref{fig:gotree}.
<<psoptions,results=hide,echo=FALSE>>=
ps.options(fonts=c("serif", "mono"))
@
<<GOtreeplot,eval=FALSE>>=
library(GO.db)
GO <- ISAGO(modules)
gog <- gograph(summary(GO$CC)[[3]])
summary(gog)
gographPlot(gog)
@ 
\begin{figure}
\centering
<<GOtreeplot-real,fig=TRUE,width=10,height=4,echo=FALSE>>=
<<GOtreeplot>>
@
\caption{Part of the Gene Ontology tree, Cellular Components ontology.
  The plot includes all terms with significant enrichment for the
  second module, and their parent terms, up to the most general term.
}
\label{fig:gotree}
\end{figure}
